\input /Users/fred/Desktop/lptp/tex/proofmacros.tex
!title{ws6_soln}

!lemma{list:ex1}{!0!1!ex[x]!,!1!S !Tt{list}(x)!2!2}
!Pr{
$!0!1!S !Tt{list}([])!2$! by~completion.
$!0!1!ex[x]!,!1!S !Tt{list}(x)!2!2$.}
!Epr

!lemma{lista:ex2}{!0!1!ex[x]!,!1!S !Tt{lista}([x,x])!2!2}
!Pr{
$!0!1!S !Tt{lista}([!Tt{a}])!2$! by~completion.
$!0!1!S !Tt{lista}([!Tt{a},!Tt{a}])!2$! by~completion.
$!0!1!ex[x]!,!1!S !Tt{lista}([x,x])!2!2$.}
!Epr

!lemma{lista:ff}{!0!1!1!S !Tt{lista}([!Tt{b}])!2!to !bot!2}
!Pr{
!Ass{!0!1!S !Tt{lista}([!Tt{b}])!2}
$!0!1!F !Tt{lista}([!Tt{b}])!2$! by~completion.
!Eass{!0!1!1!S !Tt{lista}([!Tt{b}])!2!to !bot!2}}
!Epr

!lemma{lista:f0}{!0!1!lnot !1!S !Tt{lista}([!Tt{b}])!2!2}
!Pr{
!Con{!0!1!S !Tt{lista}([!Tt{b}])!2}
$!0!1!F !Tt{lista}([!Tt{b}])!2$! by~completion.
$!0!bot$.
!Econ{!0!1!lnot !1!S !Tt{lista}([!Tt{b}])!2!2}}
!Epr

!lemma{lista:f1}{!0!1!F !Tt{lista}([!Tt{a},!Tt{b}])!2}
!Pr{
$!0!1!F !Tt{lista}([!Tt{b}])!2$.
$!0!1!F !Tt{lista}([!Tt{a},!Tt{b}])!2$.}
!Epr

!lemma{lista:gr}{!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to gr(xs))!2!2}
!Pr{
!Ind{$!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to gr(xs))!2!2$}
!Stp{none}
!Estp{!0gr([!Tt{a}])}
!Stp{$!0gr(xs)$ and $!0!1!S !Tt{lista}(xs)!2$}
!Estp{!0gr([!Tt{a}|xs])}
!Eind}
!Epr

!lemma{lista:list}{!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!S !Tt{list}(xs)!2)!2!2}
!Pr{
!Ind{$!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!S !Tt{list}(xs)!2)!2!2$}
!Stp{none}
!Estp{!0!1!S !Tt{list}([!Tt{a}])!2}
!Stp{$!0!1!S !Tt{list}(xs)!2$ and $!0!1!S !Tt{lista}(xs)!2$}
!Estp{!0!1!S !Tt{list}([!Tt{a}|xs])!2}
!Eind}
!Epr

!lemma{lista:term}{!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!T !Tt{lista}(xs)!2)!2!2}
!Pr{
!Ind{$!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!T !Tt{lista}(xs)!2)!2!2$}
!Stp{none}
!Estp{!0!1!T !Tt{lista}([!Tt{a}])!2}
!Stp{$!0!1!T !Tt{lista}(xs)!2$ and $!0!1!S !Tt{lista}(xs)!2$}
!Estp{!0!1!T !Tt{lista}([!Tt{a}|xs])!2}
!Eind}
!Epr

!lemma{lista:list:term}{!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!T !Tt{list}(xs)!2)!2!2}
!Pr{
!Ind{$!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!T !Tt{list}(xs)!2)!2!2$}
!Stp{none}
!Estp{!0!1!T !Tt{list}([!Tt{a}])!2}
!Stp{$!0!1!T !Tt{list}(xs)!2$ and $!0!1!S !Tt{lista}(xs)!2$}
!Estp{!0!1!T !Tt{list}([!Tt{a}|xs])!2}
!Eind}
!Epr

!lemma{list:lista:term}{!0!1!all[xs]!,!1(!1!S !Tt{list}(xs)!2!to !1!T !Tt{lista}(xs)!2)!2!2}
!Pr{
!Ind{$!0!1!all[xs]!,!1(!1!S !Tt{list}(xs)!2!to !1!T !Tt{lista}(xs)!2)!2!2$}
!Stp{none}
!Estp{!0!1!T !Tt{lista}([])!2}
!Stp{$!0!1!T !Tt{lista}(xs)!2$ and $!0!1!S !Tt{list}(xs)!2$}
!Estp{!0!1!T !Tt{lista}([x|xs])!2}
!Eind}
!Epr

!lemma{lista:lista}{!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!S !Tt{lista}([!Tt{a}|xs])!2)!2!2}

!lemma{lista:member:term}{!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!T !Tt{member}(!Tt{a},xs)!2)!2!2}
!Pr{
!Ind{$!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!T !Tt{member}(!Tt{a},xs)!2)!2!2$}
!Stp{none}
!Estp{!0!1!T !Tt{member}(!Tt{a},[!Tt{a}])!2}
!Stp{$!0!1!T !Tt{member}(!Tt{a},xs)!2$ and $!0!1!S !Tt{lista}(xs)!2$}
!Estp{!0!1!T !Tt{member}(!Tt{a},[!Tt{a}|xs])!2}
!Eind}
!Epr

!lemma{lista:member:succ}{!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!S !Tt{member}(!Tt{a},xs)!2)!2!2}
!Pr{
!Ind{$!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!S !Tt{member}(!Tt{a},xs)!2)!2!2$}
!Stp{none}
!Estp{!0!1!S !Tt{member}(!Tt{a},[!Tt{a}])!2}
!Stp{$!0!1!S !Tt{member}(!Tt{a},xs)!2$ and $!0!1!S !Tt{lista}(xs)!2$}
!Estp{!0!1!S !Tt{member}(!Tt{a},[!Tt{a}|xs])!2}
!Eind}
!Epr

!lemma{mema}{!0!1!all[x]!,!1(!1!S !Tt{member}(x,[!Tt{a}])!2!to x !eq !Tt{a})!2!2}
!Pr{
!Ass{!0!1!S !Tt{member}(x,[!Tt{a}])!2}
$!0!1!D !1!S !Tt{member}(x,[!Tt{a}])!2!2$! by~completion.
!Cas{!0x !eq !Tt{a}}
!Ecas
!Cas{!0!1!S !Tt{member}(x,[])!2}
$!0!1!D !1!S !Tt{member}(x,[])!2!2$! by~completion.
$!0!bot$.
!Ecas
!Fin{!0x !eq !Tt{a}}
!Eass{!0!1!1!S !Tt{member}(x,[!Tt{a}])!2!to x !eq !Tt{a}!2}}
!Epr

!lemma{lista:app}{!0!1!all[x,xs]!,!1(!1!1!S !Tt{lista}(xs)!2!land !1!S !Tt{member}(x,xs)!2!2!to x !eq !Tt{a})!2!2}
!Pr{
!Ind{$!0!1!all[xs]!,!1(!1!S !Tt{lista}(xs)!2!to !1!all[x]!,!1(!1!S !Tt{member}(x,xs)!2!to x !eq !Tt{a})!2!2)!2!2$}
!Stp{none}
!Ass{!0!1!S !Tt{member}(x,[!Tt{a}])!2}
$!0x !eq !Tt{a}$!by{Lemma}{mema}.
!Eass{!0!1!1!S !Tt{member}(x,[!Tt{a}])!2!to x !eq !Tt{a}!2}
!Estp{!0!1!all[x]!,!1(!1!S !Tt{member}(x,[!Tt{a}])!2!to x !eq !Tt{a})!2!2}
!Stp{$!0!1!all[x]!,!1(!1!S !Tt{member}(x,xs)!2!to x !eq !Tt{a})!2!2$ and $!0!1!S !Tt{lista}(xs)!2$}
!Ass{!0!1!S !Tt{member}(x,[!Tt{a}|xs])!2}
$!0!1!D !1!S !Tt{member}(x,[!Tt{a}|xs])!2!2$! by~completion.
!Cas{!0x !eq !Tt{a}}
!Ecas
!Cas{!0!1!S !Tt{member}(x,xs)!2}
!Ecas
!Fin{!0x !eq !Tt{a}}
!Eass{!0!1!1!S !Tt{member}(x,[!Tt{a}|xs])!2!to x !eq !Tt{a}!2}
!Estp{!0!1!all[x]!,!1(!1!S !Tt{member}(x,[!Tt{a}|xs])!2!to x !eq !Tt{a})!2!2}
!Eind}
!Epr

!end
